### 2020-02-24 thesis/paper.tex
user testing

With this knowledge, the clusterings were re-computed only using $k$ in the range $2$ to $10$.

>>>>

With this knowledge, the clusterings were re-computed only using $k$ in the range $2$ to $10$. The resulting reachability plot now more clearly shows robust groups of solutions, the threshold choice of the user can be seen in Figure \ref{fig:user_qcm_optics2}.

\begin{figure}[h]
	\centering
	\includegraphics[scale=.5]{user_qcm_optics2}
	\caption{OPTICS Plot after improved Sampling}
	\label{fig:user_qcm_optics2}
\end{figure}

For deciding on the final solution, he applied the default consensus function and obtained 5 results, one for each meta-cluster. From these solutions he chose the one resulting from the largest meta-cluster, with the reasoning that the threshold definition found it to be the largest group of robust solutions. The chosen result included 5 clusters which the user claimed to be the number of types of alcohol in the data-set. Not only is this the right number of clusters, the obtained result is $100\% $ equivalent to the ground truth. He also observed that the next largest meta-cluster produced a result where two clusters were merged into one. When visually inspecting the first and second result it also seems that this merging could be a sensible choice.
